\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-11 docs/paper.tex
Add more introduction

Domain names were originally designed to support only ASCII characters.
The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.
In this paper, we would analyze XXX top level .com domain by the means of clustering possible homograph domains and classify the owner of them.

>>>>

Domain names were originally designed to support only ASCII characters.
The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.

In this paper, we would analyze XXX top level .com domain by means of clustering possible homograph domains and classifying the owner of them.
In section 2, we talked about the background and history of Internationalied Domain Name (IDN) and the vulnerability behind it.
In section 3, several relevant researches are briefly introduced, which provide a couple of possible solutions to address IDN homograph attack.
We will also present the IDN policies of current major browsers in this section.
Section 4 describes the methodology of data collection and analysis we adopt in this project.
In the next section, we comment on different analysis results and explain the consequences of caveats.
For the last section, we briefly explain the ethical considerations of the research.
